Wigglyhedra

### 2025-01-07 MZ/answerReferee.tex

\item \textsl{\color{gray} Complexes associated to curves and extensions in the linear heart: This is perhaps more pedantic, but I think it is nonetheless important. I believe that under your definition, every curve, and in particular every wiggly arc, is only associated with a complex up to overall shifts in internal (path length) and homological gradings. While I understood that many of the claims involving these objects should be implicitly considered “up to both gradings shifts”, I think the claims would benefit from a more precise wording. For example, Proposition 94 as it currently is can be confusing and is falsifiable. For concreteness take $n = 1$ and the arcs $\alpha := (0, 1, \emptyset, \emptyset)$ and $\alpha' := (1, 2, \emptyset, \emptyset)$, which are not compatible (non-pointed). If I were to pick $X := P_1$ and $X' := P_2$, then $\mathrm{Ext}^1(X, X') = 0$ in $A_2$, which contradicts Proposition 94. Of course there are ``better'' choices of $X$ and $X'$, which would make the statement true. One way to correctly state it would be, e.g. ``$\mathrm{Ext}^1(X,X') = 0$ for all representatives $X$ and $X'$ of $\alpha$ and $\alpha'$ respectively''. Similar issue appears in Proposition 97, where as is currently stated, there may or may not be an extension depending on the choice of $X, X', Y, Y'$.} \\
  Thank you for catching this. Indeed, it was written imprecisely in the previous version.
  The correct functor to use here is not \(\mathrm{Ext}^1\), but rather a direct sum over \(\mathrm{Ext}^1\)s from \(X\) to all level-zero shifts of \(X'\).
  This has been corrected along the lines you suggested, and the new functor is denoted \(\mathbb{E}^1\).

@@

\item \textsl{\color{gray} pg.\,17 (C3): Unintended capitalisation: should be $g(T)$.} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,18 (C1): I think $1$ and $-1$ should be $2$ and $-2$ respectively.} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,26 (C1): The definition of zigzag algebra as it is would not be correct for $m = 2$; adding in the relation (superfluous for $m > 2$) ``all paths of length $3$ and above are killed'' should suffice.} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,27 (C1): I'd add the adjective ``full''.} \\
  Thanks! Fixed. However, we have changed the Definition 84, and the category is now defined as the bounded homotopy category of projective modules.
  The statement that it is a full subcategory of \(D^b(A_m\mathrm{-mod})\) is now written as a remark after this definition.

\item \textsl{\color{gray} pg.\,29 (C1): Given your setting, I assume you meant ``derived category'' instead?} \\
We believe this should be left as-is. Definition 84 has been updated to better match the wording in this figure.

### 2025-01-07 draft/wigglyhedra.tex
Made some technical changes.

We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
That is, a subcategory of the bounded derived category of finitely generated \(A_m\)-modules.
The algebra~\(A_m\), called the \defn{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
Let~\(e_i\) denote the idempotent path at the vertex \(i\), and let \((i, j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
A longer path, which is a composition of arrows, will be denoted by~\((i_1, i_2, \dots, i_n)\).

@@

Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
For any integer~\(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
There is an embedding of \(A_m\text{-mod}\) into \(D^b(A_m\text{-mod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-mod})\).

\begin{definition}
The category \(\mathcal{C}_m\) is defined to be the smallest full, isomorphism-closed triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\).
\end{definition}

>>>>

% We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
We begin by describing the category of interest, which is the bounded homotopy category of finitely-generated graded projective modules over a certain finite-dimensional algebra \(A_m\). 
It is a full subcategory of \(D^b(A_m\text{-grmod})\), the bounded derived category of finitely generated graded \(A_m\)-modules.
The algebra~\(A_m\), called the \defn{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
Let~\(e_i\) denote the idempotent path at the vertex \(i\), and let \((i, j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
A longer path, which is a composition of arrows, will be denoted by~\((i_1, i_2, \dots, i_n)\).

@@

Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
For any integer~\(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).

\begin{definition}
The category \(\mathcal{C}_m\) is defined to be the homotopy category of bounded complexes of finitely-generated graded projective \(A_m\)-modules.
\end{definition}
Note that there is an embedding of \(A_m\text{-grmod}\) into \(D^b(A_m\text{-grmod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-grmod})\).
\(\mathcal{C}_m\) is thus the smallest full triangulated subcategory of \(D^b(A_m\text{-grmod})\) containing all the objects \(P_i\langle j \rangle\).
